---
html_document: default
author: "Wei"
date: '2024-08-05'
output:
  html_document:
    df_print: paged
title: "EndMotif and Breakpoint"
---

# 1. loading library and function
```{r}
rm(list = ls())
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ROCR))
suppressPackageStartupMessages(library(pROC))
suppressPackageStartupMessages(library(caret))
suppressPackageStartupMessages(library(ggplot2))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(ggbeeswarm))
suppressPackageStartupMessages(library(pacman))
pacman::p_load(tidyverse,ggpubr,rstatix,ggsci,ggsignif,reshape2)
suppressPackageStartupMessages(library(openxlsx))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(pheatmap))
options(dplyr.summarise.inform = FALSE)

```


# 2. loading data
```{r}
data_feature <- read.xlsx("20240913-all_data_rmL.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)


predicted_data1 <- read.xlsx("D:/Desktop/项目/20240418_BC_cfDNA/02_AUC_LWJ/BC_cfDNA_20241113_model/21_Stacked_ensemble_v4/01_prediction_results.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
predicted_data2 <- read.xlsx("D:/Desktop/项目/20240418_BC_cfDNA/02_AUC_LWJ/BC_cfDNA_20241113_model/21_Stacked_ensemble_v4/02_prediction_results.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
predicted_data3 <- read.xlsx("D:/Desktop/项目/20240418_BC_cfDNA/02_AUC_LWJ/BC_cfDNA_20241113_model/21_Stacked_ensemble_v4/03_prediction_results.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
predicted_data <-bind_rows(predicted_data1, predicted_data2, predicted_data3)
colnames(predicted_data)[colnames(predicted_data)=="Group"] <- "SampleID"
colnames(predicted_data)[colnames(predicted_data)=="Predicted.Status"] <- "predicted"
colnames(predicted_data)[colnames(predicted_data)=="True.Status"] <- "actual"
colnames(predicted_data)[colnames(predicted_data)=="Malignant.Probability"] <- "predicted_prob"


all_data <- left_join(predicted_data, data_feature, by="SampleID")

```

# 2. loading data2
```{r}
#Clinical <- read_rds("/Users/xuewei/ZxProjects/20240422_CRC_cfDNA/21_Clinical_information/CRC_Clinical_info_20240730.rds")


feature_name <- read.xlsx("./Feature_id/feature.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
transposed_feature_name <- t(feature_name)
transposed_feature_name <- as.data.frame(transposed_feature_name)
transposed_feature_name <- cbind(RowName = rownames(transposed_feature_name), transposed_feature_name)

# 重置行名
rownames(transposed_feature_name) <- NULL
colnames(transposed_feature_name)[colnames(transposed_feature_name)=="1"] <- "Feature"

```
# 3. data processed
## 3.1 join
```{r}
data_feature_2 <- all_data %>% 
  dplyr::mutate(status_group = case_when(predicted == "0" ~ "Benign",
                                         predicted == "1" ~ "Malignant",
                                  )) %>% 
  distinct()
colnames(data_feature_2)[colnames(data_feature_2)=="SampleID"] <- "Sample"

```


## 3.2 calculate wilcox between Benign and Malignant, and select significant features 
```{r}
data_feature_all <- data_feature_2 %>% 
  select(status_group, F1:F9999)
# write.table(test_join_data_feature, "test_join_data_feature.txt", sep = "\t", row.names = F)

# 获取除了'Group_predicted'之外的所有列名
features <- setdiff(names(data_feature_all), "status_group")

# 初始化一个空的数据框来存储结果
data_feature_wilcox <- data.frame(Feature = character(),
                                  P_Value = numeric(),
                                  Median_Benign = numeric(),
                                  Median_Malignant = numeric(),
                                  stringsAsFactors = FALSE)

# 遍历每个特征进行Wilcoxon检验
for (feature in features) {
    # 选择Benign和Malignant组的数据
    group_Benign <- data_feature_all[data_feature_all$status_group == "Benign", feature]
    group_Malignant <- data_feature_all[data_feature_all$status_group == "Malignant", feature]
    
    # 计算中位数
    median_Benign <- median(group_Benign, na.rm = TRUE)
    median_Malignant <- median(group_Malignant, na.rm = TRUE)

    # 进行Wilcoxon秩和检验
    test_result <- wilcox.test(group_Benign, group_Malignant, exact = FALSE)

    # 保存结果到数据框
    data_feature_wilcox <- rbind(data_feature_wilcox, data.frame(Feature = feature,
                                         P_Value = test_result$p.value,
                                         Median_Benign = median_Benign,
                                         Median_Malignant = median_Malignant))
}


data_feature_wilcox2 <- data_feature_wilcox %>% 
  filter(P_Value < 0.001)

data_feature_wilcox3 <- left_join(data_feature_wilcox2,transposed_feature_name,by ="Feature")

write.csv(data_feature_wilcox3, "./wilcox/data_feature_wilcox.csv", row.names = FALSE)

```


# 10. End Motif (Top 100 features)
## 10.1 colname
```{r}
# EndMotif <- read.xlsx("/Users/xuewei/ZxProjects/20240422_CRC_cfDNA/22_AUC/Top100_features/20240628-groupD_feature_names.xlsx", sheet = 1, skipEmptyRows = FALSE, colNames = TRUE)
# colnames(EndMotif) <- c("Feature_num", "Feature_chr", "Type")
# 
# EndMotif2 <- EndMotif %>% 
#   filter(Type == "Endmotif") %>% 
#   filter(Feature_chr != "a/g") %>% 
#   unique()

```

## 10.2 data_Endmotif
```{r}

data_Endmotif <- data_feature_all %>%
  dplyr::select(status_group, F1224, F1319, F1256, F1255, F1223)
colnames(data_Endmotif) <- c("status_group", "AAGG", "CGGG", "AGGG", "AGGC", "AAGC")
data_Endmotif[, 2:6] <- scale(data_Endmotif[, 2:6])
```


## 10.3 data_Endmotif plot
```{r}
summary(data_Endmotif[data_Endmotif$status_group=="Benign",]$AAGG)
summary(data_Endmotif[data_Endmotif$status_group=="Malignant",]$AAGG)
p <- wilcox.test(data_Endmotif[data_Endmotif$status_group=="Benign",]$AAGG, data_Endmotif[data_Endmotif$status_group=="Malignant",]$AAGG)
p$p.value

# Reshape data from wide to long format
data_long <- pivot_longer(data_Endmotif, cols = c(AAGG, CGGG, AGGG, AGGC, AAGC), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$status_group),
                                levels = c("AAGG.Benign", "AAGG.Malignant", 
                                           "CGGG.Benign", "CGGG.Malignant", 
                                           "AGGG.Benign", "AGGG.Malignant",
                                           "AGGC.Benign", "AGGC.Malignant",
                                           "AAGC.Benign", "AAGC.Malignant"))

# Create a list for pairwise comparisons
comparison_list <- list(c("AAGG.Benign", "AAGG.Malignant"), 
                        c("CGGG.Benign", "CGGG.Malignant"), 
                        c("AGGG.Benign", "AGGG.Malignant"),
                        c("AGGC.Benign", "AGGC.Malignant"),
                        c("AAGC.Benign", "AAGC.Malignant"))

pdf("./wilcox/20241126_cfDNA_10_Endmotif_boxplot_v1.pdf", height=4, width=14)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = status_group)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_violin(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.53, color = "black", size = 4) + 
  theme_classic() +
  # theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies", fill = "") +
  scale_fill_manual(values = c("Benign" = "#7897BE", "Malignant" = "#BD7D76")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Benign|\\.Malignant", "", x))  # Simplify x-axis labels
dev.off()

```

```{r}
data_long <- pivot_longer(data_Endmotif, cols = c("AAGG", "CGGG", "AGGG", "AGGC", "AAGC"), names_to = "Measure", values_to = "Value")

data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$status_group),
                                levels = c("AAGG.Benign", "AAGG.Malignant", 
                                           "CGGG.Benign", "CGGG.Malignant", 
                                           "AGGG.Benign", "AGGG.Malignant",
                                           "AGGC.Benign", "AGGC.Malignant",
                                           "AAGC.Benign", "AAGC.Malignant"
                                           ))

data_long <- data_long %>%
  filter(!is.na(Group_Order))


data_long$type = factor(data_long$status_group, levels=c("Malignant","Benign"))

PLOT_DATA <- ggplot(data_long, aes(x = Measure, y = Value, fill = status_group, color = status_group)) + 
  geom_boxplot(width = 0.4, size = 1) +
  #stat_compare_means(aes(group = status_group), label = "p.format", size = 8, method = "wilcox.test", step.increase = 0.05) +
  theme_classic() +
  scale_fill_manual(values = c("#ADC2E0", "#DBA59E")) + # 替换填充色
  scale_color_manual(values = c("#7897BE", "#BD7D76"), guide = "none") + # 设置边框颜色，并取消图例
  guides(fill = guide_legend(override.aes = list(color = NA, size = 14, shape = 21))) + # 统一填充图例样式
  labs(x = "", y = "Frequencies", title = "", fill = "") +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.text = element_text(face = "bold", color = "black", size = 20),
    axis.line = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks.length = unit(0.5, "lines"),
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, face = "bold", color = "black", size = 24),
    axis.text.y = element_text(face = "bold", color = "black", size = 24),
    axis.title.x = element_text(face = "bold", color = "black", size = 24),
    axis.title.y = element_text(face = "bold", color = "black", size = 24)
  )

ggsave("./wilcox/20241126_cfDNA_10_Endmotif_boxplot_v3.png", PLOT_DATA, height = 7, width = 12, dpi = 300)


```


# 20. Break Point (Top 100 features)
## 20.1 data_Breakpoint
```{r}
data_Breakpoint <- data_feature_all %>% 
  dplyr::select(status_group, F1206, F1210, F1211, F1209, F1205)
colnames(data_Breakpoint) <- c("Group_predicted", "GCAGTA", "CTTGTT", "TGCGAC", "ACGACG", "AATTGC")
# write.table(data_Breakpoint, "data_Breakpoint.txt", sep = "\t", row.names = F)
data_Breakpoint[, 2:6] <- scale(data_Breakpoint[, 2:6])
```

## 20.2 data_Breakpoint plot
```{r}


# Reshape data from wide to long format
data_long <- pivot_longer(data_Breakpoint, cols = c("GCAGTA", "CTTGTT", "TGCGAC", "ACGACG", "AATTGC"), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("GCAGTA.Benign", "GCAGTA.Malignant",
                                           "CTTGTT.Benign", "CTTGTT.Malignant",
                                           "TGCGAC.Benign", "TGCGAC.Malignant",
                                           "ACGACG.Benign", "ACGACG.Malignant",
                                           "AATTGC.Benign", "AATTGC.Malignant"
                                          ))

# Create a list for pairwise comparisons
comparison_list <- list(c("GCAGTA.Benign", "GCAGTA.Malignant"),
                        c("CTTGTT.Benign", "CTTGTT.Malignant"),
                        c("TGCGAC.Benign", "TGCGAC.Malignant"),
                        c("ACGACG.Benign", "ACGACG.Malignant"),
                        c("AATTGC.Benign", "AATTGC.Malignant"))

pdf("./wilcox/20241126_cfDNA_11_Breakpoint_boxplot_v1.pdf", height=4.5, width=20)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.51, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies (%)", fill = "") +
  scale_fill_manual(values = c("Benign" = "#7897BE", "Malignant" = "#BD7D76")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Benign|\\.Malignant", "", x))  # Simplify x-axis labels
dev.off()

```

```{r}
data_long <- pivot_longer(data_Breakpoint, cols = c("GCAGTA", "CTTGTT", "TGCGAC", "ACGACG", "AATTGC"), names_to = "Measure", values_to = "Value")

data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("GCAGTA.Benign", "GCAGTA.Malignant",
                                           "CTTGTT.Benign", "CTTGTT.Malignant",
                                           "TGCGAC.Benign", "TGCGAC.Malignant",
                                           "ACGACG.Benign", "ACGACG.Malignant",
                                           "AATTGC.Benign", "AATTGC.Malignant"
                                           ))

data_long <- data_long %>%
  filter(!is.na(Group_Order))


data_long$type = factor(data_long$Group_predicted, levels=c("Benign", "Malignant"))

PLOT_DATA <- ggplot(data_long, aes(x = Measure, y = Value, fill = Group_predicted, color = Group_predicted)) + 
  geom_boxplot(width = 0.4, size = 1) +
  #stat_compare_means(aes(group = Group_predicted), label = "p.format", size = 8, method = "wilcox.test", step.increase = 0.05) +
  theme_classic() +
  scale_fill_manual(values = c("#ADC2E0", "#DBA59E")) + # 替换填充色
  scale_color_manual(values = c("#7897BE", "#BD7D76"), guide = "none") + # 设置边框颜色，并取消图例
  guides(fill = guide_legend(override.aes = list(color = NA, size = 14, shape = 21))) + # 统一填充图例样式
  labs(x = "", y = "Frequencies", title = "", fill = "") +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.text = element_text(face = "bold", color = "black", size = 20),
    axis.line = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks.length = unit(0.5, "lines"),
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, face = "bold", color = "black", size = 24),
    axis.text.y = element_text(face = "bold", color = "black", size = 24),
    axis.title.x = element_text(face = "bold", color = "black", size = 24),
    axis.title.y = element_text(face = "bold", color = "black", size = 24)
  )

ggsave("./wilcox/20241126_cfDNA_11_Endmotif_boxplot_v3.png", PLOT_DATA, height = 7, width = 12, dpi = 300)


```
## 20.1 data_Breakpoint
```{r}
data_Breakpoint_2 <- data_feature_all %>% 
  dplyr::select(status_group, F9501, F9576, F9532, F9534, F9427)
colnames(data_Breakpoint_2) <- c("Group_predicted", "MER45C", "MER65-int", "MER52A", "MER52D", "MER110")
# write.table(data_Breakpoint, "data_Breakpoint.txt", sep = "\t", row.names = F)
data_Breakpoint_2[, 2:6] <- scale(data_Breakpoint_2[, 2:6])
```

## 20.2 data_Breakpoint plot
```{r}
# Reshape data from wide to long format
data_long <- pivot_longer(data_Breakpoint_2, cols = c("MER45C", "MER65-int", "MER52A", "MER52D", "MER110"), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("MER45C.Benign", "MER45C.Malignant",
                                           "MER65-int.Benign", "MER65-int.Malignant",
                                           "MER52A.Benign", "MER52A.Malignant",
                                           "MER52D.Benign", "MER52D.Malignant",
                                           "MER110.Benign", "MER110.Malignant"))

# Create a list for pairwise comparisons
comparison_list <- list(c("MER45C.Benign", "MER45C.Malignant"),
                        c("MER65-int.Benign", "MER65-int.Malignant"),
                        c("MER52A.Benign", "MER52A.Malignant"),
                        c("MER52D.Benign", "MER52D.Malignant"),
                        c("MER110.Benign", "MER110.Malignant"))

pdf("./wilcox/20241126_cfDNA_12_Breakpoint_boxplot_v1.pdf", height=7, width=17)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.51, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies", fill = "") +
  scale_fill_manual(values = c("Benign" = "#7897BE", "Malignant" = "#BD7D76")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Benign|\\.Malignant", "", x))  # Simplify x-axis labels
dev.off()

```

```{r}
data_long <- pivot_longer(data_Breakpoint_2, cols = c("MER45C", "MER65-int", "MER52A", "MER52D", "MER110"), names_to = "Measure", values_to = "Value")

data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("MER45C.Benign", "MER45C.Malignant",
                                           "MER65-int.Benign", "MER65-int.Malignant",
                                           "MER52A.Benign", "MER52A.Malignant",
                                           "MER52D.Benign", "MER52D.Malignant",
                                           "MER110.Benign", "MER110.Malignant"
                                           ))

data_long <- data_long %>%
  filter(!is.na(Group_Order))


data_long$type = factor(data_long$Group_predicted, levels=c("Benign", "Malignant"))

PLOT_DATA <- ggplot(data_long, aes(x = Measure, y = Value, fill = Group_predicted, color = Group_predicted)) + 
  geom_boxplot(width = 0.4, size = 1) +
  #stat_compare_means(aes(group = Group_predicted), label = "p.format", size = 8, method = "wilcox.test", step.increase = 0.05) +
  theme_classic() +
  scale_fill_manual(values = c("#ADC2E0", "#DBA59E")) + # 替换填充色
  scale_color_manual(values = c("#7897BE", "#BD7D76"), guide = "none") + # 设置边框颜色，并取消图例
  guides(fill = guide_legend(override.aes = list(color = NA, size = 14, shape = 21))) + # 统一填充图例样式
  labs(x = "", y = "Frequencies", title = "", fill = "") +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.text = element_text(face = "bold", color = "black", size = 20),
    axis.line = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks.length = unit(0.5, "lines"),
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, face = "bold", color = "black", size = 24),
    axis.text.y = element_text(face = "bold", color = "black", size = 24),
    axis.title.x = element_text(face = "bold", color = "black", size = 24),
    axis.title.y = element_text(face = "bold", color = "black", size = 24)
  )

ggsave("./wilcox/20241126_cfDNA_12_Endmotif_boxplot_v3.png", PLOT_DATA, height = 7, width = 12, dpi = 300)


```

```{r}
data_Breakpoint_3 <- data_feature_all %>% 
  dplyr::select(status_group, F8781, F8744, F8782, F8761, F8755)
colnames(data_Breakpoint_3) <- c("Group_predicted", "AluYk2", "AluSc", "AluYk3", "AluY", "AluSx")
data_Breakpoint_3[, 2:6] <- scale(data_Breakpoint_3[, 2:6])
```

## 20.2 data_Breakpoint plot
```{r}
# Reshape data from wide to long format
data_long <- pivot_longer(data_Breakpoint_3, cols = c("AluYk2", "AluSc", "AluYk3", "AluY", "AluSx"), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("AluYk2.Benign", "AluYk2.Malignant",
                                           "AluSc.Benign", "AluSc.Malignant",
                                           "AluYk3.Benign", "AluYk3.Malignant",
                                           "AluY.Benign", "AluY.Malignant",
                                           "AluSx.Benign", "AluSx.Malignant"))

# Create a list for pairwise comparisons
comparison_list <- list(c("AluYk2.Benign", "AluYk2.Malignant"),
                        c("AluSc.Benign", "AluSc.Malignant"),
                        c("AluYk3.Benign", "AluYk3.Malignant"),
                        c("AluY.Benign", "AluY.Malignant"),
                        c("AluSx.Benign", "AluSx.Malignant"))

pdf("./wilcox/20241126_cfDNA_13_Breakpoint_boxplot_v1.pdf", height=6, width=18)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.7, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies", fill = "") +
  scale_fill_manual(values = c("Benign" = "#7897BE", "Malignant" = "#BD7D76")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Benign|\\.Malignant", "", x))  # Simplify x-axis labels
dev.off()

```

```{r}
data_long <- pivot_longer(data_Breakpoint_3, cols = c("AluYk2", "AluSc", "AluYk3", "AluY", "AluSx"), names_to = "Measure", values_to = "Value")

data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("AluYk2.Benign", "AluYk2.Malignant",
                                           "AluSc.Benign", "AluSc.Malignant",
                                           "AluYk3.Benign", "AluYk3.Malignant",
                                           "AluY.Benign", "AluY.Malignant",
                                           "AluSx.Benign", "AluSx.Malignant"
                                           ))

data_long <- data_long %>%
  filter(!is.na(Group_Order))

data_long$type = factor(data_long$Group_predicted, levels=c("Benign", "Malignant"))

PLOT_DATA <- ggplot(data_long, aes(x = Measure, y = Value, fill = Group_predicted, color = Group_predicted)) + 
  geom_boxplot(width = 0.4, size = 1) +
  #stat_compare_means(aes(group = Group_predicted), label = "p.format", size = 8, method = "wilcox.test", step.increase = 0.05) +
  theme_classic() +
  scale_fill_manual(values = c("#ADC2E0", "#DBA59E")) + # 替换填充色
  scale_color_manual(values = c("#7897BE", "#BD7D76"), guide = "none") + # 设置边框颜色，并取消图例
  guides(fill = guide_legend(override.aes = list(color = NA, size = 14, shape = 21))) + # 统一填充图例样式
  labs(x = "", y = "Frequencies", title = "", fill = "") +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.text = element_text(face = "bold", color = "black", size = 20),
    axis.line = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks.length = unit(0.5, "lines"),
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, face = "bold", color = "black", size = 24),
    axis.text.y = element_text(face = "bold", color = "black", size = 24),
    axis.title.x = element_text(face = "bold", color = "black", size = 24),
    axis.title.y = element_text(face = "bold", color = "black", size = 24)
  )

ggsave("./wilcox/20241126_cfDNA_13_Endmotif_boxplot_v3.png", PLOT_DATA, height = 7, width = 12, dpi = 300)


```
##
```{r}
data_Breakpoint_4 <- data_feature_all %>% 
  dplyr::select(status_group, F8690, F8696, F8693, F8695)
colnames(data_Breakpoint_4) <- c("Group_predicted", "t/c", "c/t", "a/c", "c/a")
data_Breakpoint_4[, 2:5] <- scale(data_Breakpoint_4[, 2:5])
```

## 20.2 data_Breakpoint plot
```{r}
# Reshape data from wide to long format
data_long <- pivot_longer(data_Breakpoint_4, cols = c("t/c", "c/t", "a/c", "c/a"), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("t/c.Benign", "t/c.Malignant",
                                           "c/t.Benign", "c/t.Malignant",
                                           "a/c.Benign", "a/c.Malignant",
                                           "c/a.Benign", "c/a.Malignant"))

# Create a list for pairwise comparisons
comparison_list <- list(c("t/c.Benign", "t/c.Malignant"),
                        c("c/t.Benign", "c/t.Malignant"),
                        c("a/c.Benign", "a/c.Malignant"),
                        c("c/a.Benign", "c/a.Malignant"))

pdf("./wilcox/20241126_cfDNA_14_Breakpoint4_boxplot_v1.pdf", height=6, width=18)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.7, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies", fill = "") +
  scale_fill_manual(values = c("Benign" = "#7897BE", "Malignant" = "#BD7D76")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Benign|\\.Malignant", "", x))  # Simplify x-axis labels
dev.off()

```

```{r}
data_long <- pivot_longer(data_Breakpoint_4, cols = c("t/c", "c/t", "a/c", "c/a"), names_to = "Measure", values_to = "Value")

data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("t/c.Benign", "t/c.Malignant",
                                           "c/t.Benign", "c/t.Malignant",
                                           "a/c.Benign", "a/c.Malignant",
                                           "c/a.Benign", "c/a.Malignant"
                                           ))

data_long <- data_long %>%
  filter(!is.na(Group_Order))

data_long$type = factor(data_long$Group_predicted, levels=c("Benign", "Malignant"))

PLOT_DATA <- ggplot(data_long, aes(x = Measure, y = Value, fill = Group_predicted, color = Group_predicted)) + 
  geom_boxplot(width = 0.4, size = 1) +
  #stat_compare_means(aes(group = Group_predicted), label = "p.format", size = 8, method = "wilcox.test", step.increase = 0.05) +
  theme_classic() +
  scale_fill_manual(values = c("#ADC2E0", "#DBA59E")) + # 替换填充色
  scale_color_manual(values = c("#7897BE", "#BD7D76"), guide = "none") + # 设置边框颜色，并取消图例
  guides(fill = guide_legend(override.aes = list(color = NA, size = 14, shape = 21))) + # 统一填充图例样式
  labs(x = "", y = "Frequencies", title = "", fill = "") +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.text = element_text(face = "bold", color = "black", size = 20),
    axis.line = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks.length = unit(0.5, "lines"),
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, face = "bold", color = "black", size = 24),
    axis.text.y = element_text(face = "bold", color = "black", size = 24),
    axis.title.x = element_text(face = "bold", color = "black", size = 24),
    axis.title.y = element_text(face = "bold", color = "black", size = 24)
  )

ggsave("./wilcox/20241126_cfDNA_14_Endmotif_boxplot_v3.png", PLOT_DATA, height = 7, width = 12, dpi = 300)


```

```{r}
data_Breakpoint_5 <- data_feature_all %>% 
  dplyr::select(status_group, F9180, F9182, F9281, F9371, F9215)
colnames(data_Breakpoint_5) <- c("Group_predicted", "LTR12C", "LTR12E", "LTR37B", "LTR80B", "LTR1A2")
data_Breakpoint_5[, 2:6] <- scale(data_Breakpoint_5[, 2:6])
```

## 20.2 data_Breakpoint plot
```{r}
# Reshape data from wide to long format
data_long <- pivot_longer(data_Breakpoint_5, cols = c("LTR12C", "LTR12E", "LTR37B", "LTR80B", "LTR1A2"), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("LTR12C.Benign", "LTR12C.Malignant",
                                           "LTR12E.Benign", "LTR12E.Malignant",
                                           "LTR37B.Benign", "LTR37B.Malignant",
                                           "LTR80B.Benign", "LTR80B.Malignant",
                                           "LTR1A2.Benign", "LTR1A2.Malignant"))

# Create a list for pairwise comparisons
comparison_list <- list(c("LTR12C.Benign", "LTR12C.Malignant"),
                        c("LTR12E.Benign", "LTR12E.Malignant"),
                        c("LTR37B.Benign", "LTR37B.Malignant"),
                        c("LTR80B.Benign", "LTR80B.Malignant"),
                        c("LTR1A2.Benign", "LTR1A2.Malignant"))

pdf("./wilcox/20241126_cfDNA_15_Breakpoint_boxplot_v1.pdf", height=4.5, width=16)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.5, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies", fill = "") +
  scale_fill_manual(values = c("Benign" = "#7897BE", "Malignant" = "#BD7D76")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Benign|\\.Malignant", "", x))  # Simplify x-axis labels
dev.off()

```

```{r}
data_long <- pivot_longer(data_Breakpoint_5, cols = c("LTR12C", "LTR12E", "LTR37B", "LTR80B", "LTR1A2"), names_to = "Measure", values_to = "Value")

data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("LTR12C.Benign", "LTR12C.Malignant",
                                           "LTR12E.Benign", "LTR12E.Malignant",
                                           "LTR37B.Benign", "LTR37B.Malignant",
                                           "LTR80B.Benign", "LTR80B.Malignant",
                                           "LTR1A2.Benign", "LTR1A2.Malignant"
                                           ))

data_long <- data_long %>%
  filter(!is.na(Group_Order))

data_long$type = factor(data_long$Group_predicted, levels=c("Benign", "Malignant"))

PLOT_DATA <- ggplot(data_long, aes(x = Measure, y = Value, fill = Group_predicted, color = Group_predicted)) + 
  geom_boxplot(width = 0.4, size = 1) +
  #stat_compare_means(aes(group = Group_predicted), label = "p.format", size = 8, method = "wilcox.test", step.increase = 0.05) +
  theme_classic() +
  scale_fill_manual(values = c("#ADC2E0", "#DBA59E")) + # 替换填充色
  scale_color_manual(values = c("#7897BE", "#BD7D76"), guide = "none") + # 设置边框颜色，并取消图例
  guides(fill = guide_legend(override.aes = list(color = NA, size = 14, shape = 21))) + # 统一填充图例样式
  labs(x = "", y = "Frequencies", title = "", fill = "") +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.text = element_text(face = "bold", color = "black", size = 20),
    axis.line = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks.length = unit(0.5, "lines"),
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, face = "bold", color = "black", size = 24),
    axis.text.y = element_text(face = "bold", color = "black", size = 24),
    axis.title.x = element_text(face = "bold", color = "black", size = 24),
    axis.title.y = element_text(face = "bold", color = "black", size = 24)
  )

ggsave("./wilcox/20241126_cfDNA_15_Endmotif_boxplot_v3.png", PLOT_DATA, height = 7, width = 12, dpi = 300)


```

```{r}
data_Breakpoint_6 <- data_feature_all %>% 
  dplyr::select(status_group, F9823, F9812, F9803, F9822, F9831)
colnames(data_Breakpoint_6) <- c("Group_predicted", "Tigger2b_Pri", "Tigger18a", "Tigger14a", "Tigger2a", "Tigger4b")
data_Breakpoint_6[, 2:6] <- scale(data_Breakpoint_6[, 2:6])
```


## 20.2 data_Breakpoint plot
```{r}

# Reshape data from wide to long format
data_long <- pivot_longer(data_Breakpoint_6, cols = c("Tigger2b_Pri", "Tigger18a", "Tigger14a", "Tigger2a", "Tigger4b"), names_to = "Measure", values_to = "Value")

# Create a new factor to control the order of the x-axis
data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("Tigger2b_Pri.Benign", "Tigger2b_Pri.Malignant",
                                           "Tigger18a.Benign", "Tigger18a.Malignant",
                                           "Tigger14a.Benign", "Tigger14a.Malignant",
                                           "Tigger2a.Benign", "Tigger2a.Malignant",
                                           "Tigger4b.Benign", "Tigger4b.Malignant"))

# Create a list for pairwise comparisons
comparison_list <- list(c("Tigger2b_Pri.Benign", "Tigger2b_Pri.Malignant"),
                        c("Tigger18a.Benign", "Tigger18a.Malignant"),
                        c("Tigger14a.Benign", "Tigger14a.Malignant"),
                        c("Tigger2a.Benign", "Tigger2a.Malignant"),
                        c("Tigger4b.Benign", "Tigger4b.Malignant"))

pdf("./wilcox/20241126_cfDNA_16_Breakpoint_boxplot_v1.pdf", height=4.5, width=6)
# Plot
ggplot(data_long, aes(x = Group_Order, y = Value, fill = Group_predicted)) +
  geom_boxplot(width = 0.4, size = 1) +
  # geom_quasirandom(width = 0.1, varwidth = TRUE, cex = 2, method = "quasirandom")+
  geom_signif(comparisons = comparison_list, 
              test = "wilcox.test",
              map_signif_level = TRUE) +
  stat_summary(fun = median, geom = "text", 
               aes(label = sprintf("%0.3f", after_stat(y))),
               vjust = 0.5, hjust = -0.6, color = "black", size = 4) + 
  theme_classic() +
  theme(legend.position = "NA") +
  labs(title = "", x = NULL, y = "Frequencies", fill = "") +
  scale_fill_manual(values = c("Benign" = "#7897BE", "Malignant" = "#BD7D76")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "bold", color = "black", size = 12),
        axis.text.y = element_text(face = "bold", color = "black", size = 12),
        axis.title.x = element_text(face = "bold", color = "black", size = 12),
        axis.title.y = element_text(face = "bold", color = "black", size = 12),
        # legend.position = "none",
        panel.grid = element_blank(),
        axis.line = element_line(linewidth = 0.5, colour = "black"),
        axis.ticks = element_line(linewidth = 0.5, colour = "black"), axis.ticks.length = unit(0.5, "lines")) +
  scale_x_discrete(labels = function(x) gsub("\\.Benign|\\.Malignant", "", x))  # Simplify x-axis labels
dev.off()

```


```{r}
data_long <- pivot_longer(data_Breakpoint_6, cols = c("Tigger2b_Pri", "Tigger18a", "Tigger14a", "Tigger2a", "Tigger4b"), names_to = "Measure", values_to = "Value")

data_long$Group_Order <- factor(interaction(data_long$Measure, data_long$Group_predicted),
                                levels = c("Tigger2b_Pri.Benign", "Tigger2b_Pri.Malignant",
                                           "Tigger18a.Benign", "Tigger18a.Malignant",
                                           "Tigger14a.Benign", "Tigger14a.Malignant",
                                           "Tigger2a.Benign", "Tigger2a.Malignant",
                                           "Tigger4b.Benign", "Tigger4b.Malignant"
                                           ))

data_long <- data_long %>%
  filter(!is.na(Group_Order))

data_long$type = factor(data_long$Group_predicted, levels=c("Benign", "Malignant"))

PLOT_DATA <- ggplot(data_long, aes(x = Measure, y = Value, fill = Group_predicted, color = Group_predicted)) + 
  geom_boxplot(width = 0.4, size = 1) +
  #stat_compare_means(aes(group = Group_predicted), label = "p.format", size = 8, method = "wilcox.test", step.increase = 0.05) +
  
  theme_classic() +
  scale_fill_manual(values = c("#ADC2E0", "#DBA59E")) + # 替换填充色
  scale_color_manual(values = c("#7897BE", "#BD7D76"), guide = "none") + # 设置边框颜色，并取消图例
  guides(fill = guide_legend(override.aes = list(color = NA, size = 14, shape = 21))) + # 统一填充图例样式
  labs(x = "", y = "Frequencies", title = "", fill = "") +
  theme(
    legend.position = "right",
    legend.title = element_blank(),
    legend.text = element_text(face = "bold", color = "black", size = 20),
    axis.line = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks = element_line(linewidth = 0.5, colour = "black"),
    axis.ticks.length = unit(0.5, "lines"),
    axis.text.x = element_text(angle = 0, vjust = 0.5, hjust = 0.5, face = "bold", color = "black", size = 24),
    axis.text.y = element_text(face = "bold", color = "black", size = 24),
    axis.title.x = element_text(face = "bold", color = "black", size = 24),
    axis.title.y = element_text(face = "bold", color = "black", size = 24)
  )

ggsave("./wilcox/20241126_cfDNA_16_Endmotif_boxplot_v3.png", PLOT_DATA, height = 7, width = 14, dpi = 300)


```




# 30. Top 30 features
## 30.1 colname
```{r}
data_feature_wilcox3_max30 <- data_feature_wilcox3 %>% 
  mutate(ratio = Median_Benign/ Median_Malignant) %>% 
  arrange(ratio) %>% 
  slice_max(n = 30, order_by = ratio)

data_feature_wilcox3_min30 <- data_feature_wilcox3 %>% 
  mutate(ratio = Median_Benign/ Median_Malignant) %>% 
  arrange(ratio) %>% 
  slice_min(n = 30, order_by = ratio)

data_feature_wilcox4 <- rbind(data_feature_wilcox3_max30, data_feature_wilcox3_min30)

```

## 30.2 data_feature_100
```{r}
# join_data_feature %>%
#   group_by(OS_time) %>%
#   summarise(count = n())

Feature_num <- data_feature_wilcox4$Feature

data_feature_100 <- data_feature_2 %>% 
  dplyr::select(Sample, status_group, data_feature_wilcox4$Feature)

# write.table(data_feature_100, "data_feature_100.txt", sep = "\t", row.names = F)

```


## 30.3. data_feature_100 plot
```{r}
library(dplyr)
data_feature_100 <- data_feature_100 %>% 
  arrange(status_group)

# 保存样本名称和预测组别信息，以便后续使用
sample_info <- data_feature_100[, c("Sample", "status_group")]

# 计算z-score，注意排除第一列（Sample）和Group_predicted列
# data_z <- t(scale(t(data_feature_100[, !names(data_feature_100) %in% c("Sample", "Group_predicted")])))
data_z <- scale(data_feature_100[, !names(data_feature_100) %in% c("Sample", "status_group")])

# 转换回数据框，并添加样本和组别信息
data_z <- data.frame(Sample = sample_info$Sample, 
                     status_group = sample_info$status_group, 
                     data_z)

# annotation_row
annotation_row = data.frame(
  Group = factor(data_z$status_group)
)
rownames(annotation_row) = data_z$Sample

# annotation_colors
ann_colors = list(
  Group = c('Benign' = "#7897BE", 'Malignant' = "#BD7D76")
)

pheatmap_data_z <- data_z %>% 
  select(-status_group) %>%
  column_to_rownames(var = "Sample")


pheatmap_data_z <- pheatmap_data_z %>%
  dplyr::select(-F6922, -F6921, -F3522, -F3316, -F3465, -F3317,-F3044)

pdf("./wilcox/20241126_cfDNA_17_feature_100_pheatmap_v1.pdf", height=4, width=8)

pheatmap(pheatmap_data_z, 
         color = colorRampPalette(c("#0000cd","#FFFFFF","#ff3c00"))(100)[0:100], 
         fontsize=9, 
         fontsize_row=9, 
         # display_numbers = matrix(ifelse(copper_pheatmap2 > 1, "*", ""), nrow(copper_pheatmap2)),
         breaks = seq(-5,5,1/10), legend_breaks = seq(-5,5,2.5),
         annotation_row = annotation_row, 
         annotation_colors = ann_colors, 
         cluster_rows=F, 
         cluster_cols=T,
         border_color = NA,
         show_rownames = FALSE,  # 隐藏纵坐标标签
         show_colnames = FALSE)
dev.off()

```


